---
title: "ggplot2 Tutorial From ODSC East"
author: "Sathish Thiyagarajan"
date: "May 24, 2016"
output: html_document
---

### Simple ggplot2 script


Loading ggplot2! We are going to use the diamonds dataset.
We make a simple plot first.

```{r}
library(ggplot2)
library(RColorBrewer)
data(diamonds)
plot(price ~ carat, data=diamonds)
```

Let's make the plot prettier using ggplot2.

```{r}
ggplot(data=diamonds,aes(x=carat,y=price)) + geom_point(color='red')
```

Let's now vary the color according to the cut of the diamond

```{r,out.width = '500px', dpi=200}
ggplot(data=diamonds,aes(x=carat,y=price)) + geom_point(aes(color=cut))
```

Let's make a histogram of the price now.

```{r}
ggplot(diamonds) + geom_histogram(aes(x=price),fill='red',binwidth=500)
```

We can also make a density plot.

```{r}
ggplot(diamonds) + geom_density(aes(x=price),fill='grey50',color='red')
```

Making a plot with a smoothing line.

```{r}
ggplot(diamonds,aes(x=carat,y=price)) + geom_point() + geom_smooth()
```

Make several lines with multicolor plots.

```{r}
ggplot(diamonds,aes(x=carat,y=price,color=cut)) + geom_point() + 
  geom_smooth() + scale_color_brewer(palette="Set1")
```

If colors are applied later, the lines are changed
```{r}
ggplot(diamonds,aes(x=carat,y=price)) + geom_point(aes(color=cut)) + 
  geom_smooth() + scale_color_brewer(palette="Set1")
```

Make a group of plots
```{r}
ggplot(diamonds,aes(x=carat,y=price)) + geom_point() + 
  facet_wrap(~cut,ncol=1)
```

Make a group of histograms
```{r}
ggplot(diamonds,aes(x=carat)) + geom_histogram() + facet_wrap(~cut)
```

Make a group of violins
```{r}
ggplot(diamonds,aes(factor(cut),y=price)) +
  geom_violin() + geom_jitter(width = 0.1) + xlab('cut')
```
